Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-11-27 paper/sheaf_lics.tex
[grammar] Allow to => allow one to

Also proposition truncation could be seen as a primitive type former
in homotopy type theory, it can be defined using higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher}. We adopt this
point of view as it allows to maintain the slogan that homotopy type
theory is type theory plus univalence and higher inductive types.
%

@@

Note that similar notion of modal operator have been already studied
extensively in non-dependent type
theory~(see \eg \cite{benton1998computational}). In those works, they connect
modalities to computational monad in programming
languages~\cite{moggi-monad}. However, in our setting, modalities
correspond to idempotent monads, a property that is rarely true 
in functional programming, except for the identity monad of course.

@@

The proof is based on the following central result.
\begin{lem}
  Let $X:\Type_p$, $Y:\Type_p^\modal$ and $f:X\to Y$. If for all $y:Y$,
  $\modal (\fib f y)$ is contractible, then $\modal X = Y$.
\end{lem}
%
It is straighforward to define a map
$$\phi:\sum_{x:X}  (f x = y)\to
\sum_{x:\modal X} (\modal f x = \eta_Y y),$$
using $\eta$ functions.
We just need to check that every $\modal(\fib \phi {x;p})$ is
contractible.
Technical transformations allow to prove
$$\fib\phi{x;p} = \fib s {y;p^{-1}}$$
for some $a:\modal X$, $b:\modal Y$ and 
$$s:\fib{\eta_X}a \to \fib{\eta_Y}b.$$
%
From definition of left exactness, one can deduce the following:
\begin{lem}
  Let $A,B:\Type_p$. Let $f:A\to B$. If $\modal A$ and $\modal B$ are
  contractible, then so is $\fib f b$ for any $b:B$.
\end{lem}
Thus, we just need to prove that $\modal(\fib {\eta_X} a)$ and
$\modal(\fib {\eta_Y} b)$ are contractible.
But we have the lemma:
\begin{lem}
  Let $A:\Type_p$. Then for any $y:\modal A$, $\modal(\fib {\eta_A}
  y)$ is contractible.
\end{lem}

>>>>

Also proposition truncation could be seen as a primitive type former
in homotopy type theory, it can be defined using higher inductive
types~\cite{lumsdaine2011higher,lumsdaine2013higher}. We adopt this
point of view as it allows one to maintain the slogan that homotopy type
theory is type theory plus univalence and higher inductive types.
%

@@

Note that similar notion of modal operator have been already studied
extensively in non-dependent type
theory~(see \eg \cite{benton1998computational}). In those works, they connect
modalities to computational monads in programming
languages~\cite{moggi-monad}. However, in our setting, modalities
correspond to idempotent monads, a property that is rarely true 
in functional programming, except for the identity monad of course.

@@

The proof is based on the following central result.
\begin{lem}
  Let $X:\Type_p$, $Y:\Type_p^\modal$ and $f:X\to Y$. If for all $y:Y$,
  $\modal (\fib f y)$ is contractible, then $\modal X = Y$.
\end{lem}
%
It is straighforward to define a map
$$\phi:\sum_{x:X}  (f x = y)\to
\sum_{x:\modal X} (\modal f x = \eta_Y y),$$
using $\eta$ functions.
We just need to check that every $\modal(\fib \phi {x;p})$ is
contractible.
Technical transformations allow one to prove
$$\fib\phi{x;p} = \fib s {y;p^{-1}}$$
for some $a:\modal X$, $b:\modal Y$ and 
$$s:\fib{\eta_X}a \to \fib{\eta_Y}b.$$
%
From definition of left exactness, one can deduce the following:
\begin{lem}
  Let $A,B:\Type_p$. Let $f:A\to B$. If $\modal A$ and $\modal B$ are
  contractible, then so is $\fib f b$ for any $b:B$.
\end{lem}
Thus, we just need to prove that $\modal(\fib {\eta_X} a)$ and
$\modal(\fib {\eta_Y} b)$ are contractible.
But we have the lemma:
\begin{lem}
  Let $A:\Type_p$. Then for any $y:\modal A$, $\modal(\fib {\eta_A}
  y)$ is contractible.
\end{lem}
